RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-04 review/response.tex

\documentclass[10pt]{scrartcl}

\usepackage{scrletter}
\usepackage{parskip}

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
% \usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

% \usepackage{xr-hyper}
% \usepackage{hyperref}
% \makeatletter
% \long\def\myempty{}
% \def\XR@addURL#1{\XR@@dURL#1\myempty{}{}{}{}{}\\}
% \def\XR@@dURL#1#2#3#4#5#6#7\\{%
%   {#1}{#2}%
%   \ifx\myempty#6\@empty
% 	{#3}{#4}{\XR@URL}%
%   \else
%   \fi
% }
% \makeatother

\usepackage[pagewise]{lineno}
\usepackage{xr}
\externaldocument[m-]{../main}

@@

\begin{letter}{%
		Guest Editors\\
		IEEE Journal on Selected Areas in Communications
	}
	\opening{Dear Editors and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of ``RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface''.
	We would like to express our sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below, we prepare a point-to-point response and describe all the changes made to the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of JSAC publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	Although the paper presents a novel idea and tackles an interesting problem, it requires great effort to improve the presentation, the language, and the mathematical derivations. Detailed comments are given as follows:

	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
	\reply {We apologize for the mistake. The abstract and keywords have been revised to meet the specifications.}

@@

	\point The manuscript contains multiple grammatical errors and unclear sentences that require correction. Please revise the manuscript for improved clarity. For instance, in the first paragraph of Section II, Subsection B, the sentence "It is assumed that the signal reflected by two or more times is negligible" is not clear.
	\reply {We have thoroughly revised the manuscript to address the grammatical errors and improve sentence clarity. The example sentence has been revised to ``It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.''}

	\point Please consider defining all acronyms (e.g., MRC) and all the notations in Section I (e.g., the mutual information, probabilities, etc.,).
	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper. Due to the space limitation, the list is not included but have carefully defined all acronyms and notations before their first usage. We appreciate your understanding in this matter.}

	\point Please ensure that all variables and symbols are properly defined and explained before their usage (e.g., $P$, $\sigma_1^2, \ldots, \sigma_L^2$, etc.). Also, $\mathbf{h}_E^H$ in eq. (46) is used without prior definition.
	\reply {The issue has been addressed in the revised manuscript. $\mathbf{h}_E^H$ in eq. (46) should be $\mathbf{h}^H$.}

	\point Please ensure consistency with the notation introduced in Section I throughout the manuscript. For instance, in Section II, Subsection B, after eq. (4b), the dimensions for $\mathbb{I}$ are not defined.
	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section~\ref{m-sc:introduction}. In the provided example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}

	\point To ensure consistency and clarity, please maintain uniformity in the usage of mathematical symbols and technical terms throughout the paper. For example, in eq. (3), the amplitude scattering ratio of the node is defined as $\beta_m$, while in eq. (4a), it is referred to as $\alpha_k$. Additionally, there is a discrepancy in the usage of the term 'node' throughout the manuscript and 'tag' in the appendix. Please use a consistent term to refer to the same entity throughout the entire paper to avoid confusion and improve clarity.
	\reply {Thank you for bringing this to our attention. We were trying to be rigorous and consistent with the notation used in the literature, but didn't realize the confusion it may cause to the readers. In BackCom literatures, $\alpha_k$ is a constant that measures the \emph{average} reflection efficiency (irrelevant to the state) for node $k$. In RIS literatures, $\beta_m$ measures the scattering ratio of one element at state $m$. In the revised manuscript, we have unified those notation in page~\pageref{m-eq:backscatter_modulation} and revised the term ``tag'' to ``node'' in the appendix.}

	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.
	\reply {After a careful investigation, we found there are three different definitions for the reflection coefficient in the literature:
		\begin{enumerate}
			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z}$ in overview papers \cite{VanHuynh2017,Liang2022};
			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z^*}$ in BackCom paper \cite{Boyer2014};
			\item $\Gamma_m^* = \frac{Z^* - Z_m}{Z + Z_m}$ in RF paper \cite{Hansen1989},
		\end{enumerate}
		where $Z_m$ is the load impedance at state $m$ and $Z$ is the antenna impedance.
		Unfortunately, we are not microwave engineering experts and have to guess that they may choose different parties (antenna and space) as reference. In the current version, we have not made any change to eq. (1) but would be grateful to hear your opinion on this issue.}

	\point It is unclear what is meant by relative QoS. Additionally, there is a lack of clarity regarding the derivation of eqs. (17-19) and how the relative QoS of the primary link is incorporated in those equations. The defined expressions should be clearly explained and justified. Please provide additional details and reasoning.
	\reply {We apologize for the confusion caused by poor wording. QoS refers to the relative priority of the primary link, and it should be either ``QoS'' or ``relative priority''. We have added a footnote on this. Besides, the information theory subsection (including the derivation of eqs. (17-19)) has been rewritten and incorporated into Section II.B with proper explanation. We also modified Remark \ref{m-re:dynamic_passive_beamforming} and added Remark \ref{m-re:independent_encoding} to clarify the derivation of achievable rates. Please see page~\pageref{m-re:dynamic_passive_beamforming}--\pageref{m-eq:weighted_sum_mutual_information} for details.}

	\point The link between eq. (9) and eq. (25) lacks clarity and misses intermediate steps. Also, the expression of the function $Q$ provided in eq. (25) appears to be independent of the active beamforming $\boldsymbol{w}$.  It is unclear how the derivation of $Q$ with respect to $\boldsymbol{w}$ is performed in this case. Please clarify the relationship between $Q$ and $\boldsymbol{w}$ and provide a clear derivation for better understanding. The same remark about clarity applies to eq. (28) and eq. (33).
	\reply {
		Plugging the conditional energy PDF into the DMMAC expression, we have
		\begin{equation}
			q(x_l|x_{m_{\mathcal{K}}}) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
			\label{eq:dmmac_gamma}
		\end{equation}
		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
		$Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
		\begin{equation}
			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!}.
			\label{eq:regularized_incomplete_gamma}
		\end{equation}
		In the revised manuscript, we have added the intermediate steps from (9) to (25) in page~\pageref{m-eq:dmmac_gamma} with proper details. The corresponding part has been completely rewritten to improve logic and clarity.}

@@

	\point Is the BCD algorithm convergent for the optimization problem (20)?
	\reply {The BCD algorithm is convergent for the optimization problem (20), since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality. This argument has been added prior to the convergence results in Fig. 7.}

	\point Please write the mathematical expression of eq. (40) properly. Moreover, there appears to be a mistake in the sign of the Lagrangian function of the optimization problem stated in Equation (21). If the optimization problem is intended to be a minimization problem, it should be explicitly mentioned to avoid any ambiguity or confusion.
	\reply {Problem (21) is a maximization problem and the Lagrangian function (40) has been rewritten as
		\begin{equation}
			I(x_{\mathcal{K}}) + \sum_k \nu_k \biggl( \sum_{m_k} p(x_{m_k}) - 1 \biggr) + \sum_k \sum_{m_k} \lambda_{m_k} p(x_{m_k}).
		\end{equation}
	}

	\point The expression of the primary achievable rate in eq. (37) seems to be wrong since the primary message is also included in the cascaded channel and cannot be ignored.
	\reply {We appreciate your careful reading. The primary message is indeed included in the scattered component. However, since the user decodes both links independently, the backscatter uncertainty cannot be eliminated when decoding the primary link. That is to say, the scattered component should be treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$. The same reasoning was considered in \cite{Long2020a}. We have revised the corresponding footnote \ref{m-fn:ambc} to justify this.}

	\point In Figure 7, it is unclear why the KKT, PGD, and BCD algorithms are plotted separately since the BCD algorithm encompasses both the KKT and PGD algorithms. If there is a specific reason for displaying them separately, please provide a justification to enhance the understanding of the reader. Additionally, please provide the unit for the weighted sum rate axis.
	\reply {In company with BCD, we also plotted the convergence results of KKT and PGD algorithms to show how much performance gain is provided by solving each subproblem (over the initialization method specified in the previous paragraph). We have justified this in Section~\ref{m-sc:convergence}. The unit of the y axis of Fig.~\ref{m-fg:distribution_weights} has been specified as bit/s/Hz.}

	\point Is the decoding of the backscatter information based on an energy detector reliable in this case, especially with high-order modulation or large number of scatter nodes? In other words, can the user in practice decode the backscatter information especially in the presence of the noise and signal variations due to the fading or the interference, etc.?
	\reply {The energy detector is a simple and practical method for backscatter information decoding, and its reliability is improved by the adaptive input distribution and thresholding design. With high-order modulation or large number of scatter nodes, its performance can be further enhanced by increasing the spreading factor $N$ or using stronger error correction codes with lower code-rate. In practice, the user can decode backscatter nodes ranging from few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps. We have added footnote \ref{m-fn:energy_detector} on this issue, and the reviewer is referred to Table II in \cite{Wu2022e} for more details.}

	\point In Section III, the aim is to characterize the primary-total-backscatter rate region where the user retrieves both the backscatter information and the primary message. Why is the weighted sum mutual information maximized with respect to only the input distribution of the backscatter information and not jointly with respect to the input distribution of the primary message `s' as well? In other words, is the choice of $s \sim \mathcal{CN} (0,1)$ optimal?
	\reply {This is indeed a very good question. The choice of $s \sim \mathcal{CN} (0,1)$ is generally not optimal for weighted sum mutual information. To the best of our knowledge, the optimal primary distribution in this case remains an open issue, but some insights were given in those papers:
		\begin{itemize}
			\item If there is no direct link and the node is with \emph{average} power constraint, then the optimal distribution for \emph{weighted sum mutual information} requires a time-sharing between those modes \cite{Pillai2011}:
			\begin{itemize}
				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
				\item $x$ follows zero-mean Gaussian distribution and $s$ is a constant;
				\item $s$ and $x$ equal 0.
			\end{itemize}
			\item If there is no direct link and the node is with \emph{peak} power constraint, then the optimal distribution for \emph{sum mutual information} is not unique, for example \cite{Zhang2023} (came out after our submission):
			\begin{itemize}
				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
				\item $s$ follows Rayleigh distribution and $x$ follows uniform distribution on $[0, 2 \pi)$;
			\end{itemize}
		\end{itemize}
		Despite not optimal, the assumption of Gaussian primary source and finite-support backscatter source are relatively practical and widely adopted in relevant literatures. We have added Remark~\ref{m-re:non_gaussian} on this, but intentionally avoided the discussion of optimal distribution, since it is beyond the scope of this paper and may confuse the readers. We appreciate your understanding in this matter.}

	\point In Section IV, Subsection B, it is stated that the RIS always ensures constructive superposition of direct and scattered components which is not true. The RIS can also add those components destructively which could be used for example to enhance the physical layer security of a system in the presence of an eavesdropper.
	\reply {We apologize for the oversight. The argument has been modified to ``Here, RIS ensures constructive superposition of direct and scattered components.''}
\end{reviewer}

@@

	The manuscript presents a novel concept, i.e., RIScatter, and studies an interesting problem. However, there are several problems with the manuscript, namely:

	\point Presentation and use of English: the presentation is sometimes unclear about the differences of RIScatter and existing techniques, it seems that the authors are concerned about listing the contributions in the introduction and forgot to contrast the key differences between existing approaches and the proposed RIScatter. Perhaps the authors can polish this part and make it more compact. Sometimes, a shorted and compact text can be made easier to understand. Moreover, there are too many poorly written sentences, typos and Grammar errors throughout the manuscript. It is not acceptable that a JSAC paper would feature with this level of English (especially coming from a British university!). Therefore, it is fundamental to improve the use of English and make sentences properly structured.
	\reply {We agree with the reviewer that the contrast between RIScatter and existing techniques could be clearer. The introduction and contribution have been refined in precise and explicit words for improved readability and clarity. Also, we have completely rewritten Section II.A on RIScatter principles to highlight the key differences between RIScatter and existing techniques. Remark 1 now emphasizes the distinction and relationship between RIScatter and dynamic RIS. We also apologize for the poor English usage. The manuscript has been carefully proofread and revised to address the typos and grammar errors. We believe that the revised manuscript should be much easier to understand.}

	\point Literature review: the literature review on rate characterization for backscatter communications is deficient. Some recent and closely related works are missing:
	\begin{itemize}
		\item J. Qian, Y. Zhu, C. He, F. Gao and S. Jin, "Achievable Rate and Capacity Analysis for Ambient Backscatter Communications," in IEEE Transactions on Communications, vol. 67, no. 9, pp. 6299-6310, Sept. 2019.
		\item Z. Dai, R. Li, J. Xu, Y. Zeng and S. Jin, "Rate-Region Characterization and Channel Estimation for Cell-Free Symbiotic Radio Communications," in IEEE Transactions on Communications, vol. 71, no. 2, pp. 674-687, Feb. 2023.
		\item H. E. Hassani, A. Savard, E. V. Belmega and R. C. de Lamare, "Multi-user downlink NOMA systems aided by ambient backscattering: achievable rate regions and energy-efficiency maximization," in IEEE Transactions on Green Communications and Networking, 2023.
	\end{itemize}
	\reply {We appreciate your expert and insightful comments on the reference list. Those papers have been incorporated into the revised manuscript.}

### 2023-08-04 main.tex
:speech_balloon: Update response

% siunitx
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

@@

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{section}{Introduction}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.

>>>>

@@

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{dc}{DC}{Direct Current}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{ber}{BER}{Bit Error Rate}

@@

\begin{section}{Introduction}
	\label{sc:introduction}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and rides its own information, and the co-located receiver cooperatively decodes both links.
	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.

	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	The achievable rate and optimal input distribution for binary-input \gls{ambc} are investigated in \cite{Qian2019b}, but its impact on the primary link is not considered.
	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
	Under those assumptions, the achievable rate region of cell-free \gls{sr} is characterized in \cite{Dai2023}.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.
